Polynomial phase estimation by phase unwrapping

### 2013-02-18 paper.tex
Worked out that it's the error method that has numerical difficulties, probably need to implement that with BigRational

In the analysis of most existing polynomial phase estimators it is common to make what is known as a `small noise' assumption.  This name

>>>>

The analysis of most existing polynomial phase estimators make what is known as a `small errors' or `small noise' assumption~\cite{Peleg_linear_FM,Oshea_cpf_2004,Djurovic_haf_cpf_2012}.  This amounts to assuming that that estimator $\hat{\mu}_k$ of the $k$th coefficient is such that $N^{k}(\tilde{\mu}_k -  \hat{\mu}_k) \rightarrow 0$ in probability as $N \rightarrow \infty$.  This assumption is used to justify the use of first and second order expansions~\cite{vonMises_diff_stats_1947,vanDerVart1971_asymptotic_stats}, typically called a `perturbation analysis' in this literature~\cite{Peleg_linear_FM,Porat_asympt_HAF_DPT_1996,Oshea_cpf_2004}, to obtain expression for the asymptotic mean square error of the estimator in question.  The `small errors' assumption is usually justified by numerical Monte Carlo simulations, showing the asymptotic mean square error obtained by the perturbation analysis to be accurate provided that the signal to noise ratio (SNR) is larger than a `threshold' value (see the simulations in Section~\ref{sec:simulations} for examples).  Typically one observes the threshold to move to smaller values of SNR as the $N$ increases.  The problem with the `small errors' assumption is that it is not known if the threshold continues to move to smaller and smaller values of SNR as $N$ increase or if it infact converges to some finite (but perhaps small) value of SNR, the consequence being that the estimator will be innaccurate if the SNR is smaller than this finte value, regardless of the number of observations $N$ obtained.

An analysis of the HAF estimator under the assumption that the noise $\{X_n\}$ is what and Gaussian and without the `small errors' assumption has been made in~\cite{Porat_asympt_HAF_DPT_1996}.  There does not appear to have been an analysis of any phase unwrapping estimator without the small noise assumption.  Infact, there appears to be a misconception that phase unwrapping estimators are only accurate with the noise is `small' in some sense.  The misconceptions would appear to be motivated by early papers such as~\cite{Tretter1985,Kay1989} where it was observed that the noise observed in the phase of the signal only looks `Gaussian' when the complex noise producing it has small variance.  The results
